Safe Transferable Regions

### 2015-11-17 paper/type-system.tex
section 3

The actual implementations of region-based memory management for \name
may choose to realize the $\toprgn$ as a garbage-collected region, but
this is not required. Our operational semantics
(\S\ref{sec:fb-opsem}), for example, does not even associate a region
with $\toprgn$, instead opting to allocate $\RgnZ$ objects in the same
transferable regions that they represent. Our type safety result
nonetheless guarantees memory safety in this implementation.

>>>>

%The actual implementations of region-based memory management for \name
%may choose to realize the $\toprgn$ as a garbage-collected region, but
%this is not required. Our operational semantics
%(\S\ref{sec:fb-opsem}), for example, does not even associate a region
%with $\toprgn$, instead opting to allocate $\RgnZ$ objects in the same
%transferable regions that they represent. Our type safety result
%nonetheless guarantees memory safety in this implementation.
